Git Learning Notes

### 2014-02-15 BackMatter/paper.tex
daily works

@@

The observed raman lines of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 cm. The calculated \ce{W-O} bond distance using Eq.~\ref{eq:wobond} fit very well with the crystallographic value of \ce{Na5W_{14}O_{44}}. \cite{Triantafyllou1999a} The 107 peak probably arise from \ce{Na-O} bond.

@@

@@

>>>>

An empirical formula to relate the Raman peaks and \ce{W-O} bonding lengths \cite{Hardcastle1995} is
\begin{equation}\label{eq:wobond}
\nu = 25823 \exp{-1.902\cdot R}.
\end{equation}
And the standard deviation of estimating \ce{W-O} bond distance from Raman stretching wavenumber is $\pm0.034$\AA.
The observed Raman peaks of \ce{Na5W_{14}O_{44}} phase lies at 965, 943, 913, 808, 786, 778, 765, 695 and 107 cm. Multi-peaks Lorentzian fitting is preformed to precisely determine the central maximum. Good fitting is obtained, as shown in Fig.~\ref{fig:naworamfit}. We then calculated \ce{W-O} bond distance using Eq.~\ref{eq:wobond}, as illustrated in Table~\ref{tab:nawobond}. The predicted \ce{W-O} bond length comply very well with the crystallographic value of \ce{Na5W_{14}O_{44}} phase.\cite{Triantafyllou1999a} The 107 peak probably is caused by \ce{Na-O} bond.
% Na5 raman fitting
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{naxwo_ramfit}
\caption[\ce{Na5W_{14}O_{44}} Raman fitting]{Multi-peaks Lorentzian fitting on two major peaks region of \ce{Na5W_{14}O_{44}}. The peaks sum height difference is caused by different baseline value adopted in each fitting.}
\label{fig:naworamfit}
\end{figure}

% W-O bond length
\begin{table}[htb]
\centering
\caption{\ce{W-O} bond length predication}\label{tab:nawobond}
\begin{tabular}{lccr}
\toprule
peak center & length (\AA) & peak center & length (\AA) \\
\midrule
694.6 & 1.900 &  808.6 &  1.821 \\
745.4 & 1.863 &  911.5 &  1.758 \\
764.4 & 1.850 &  933.0 &  1.745 \\
778.7 & 1.840 &   943.5 & 1.740 \\
788.4 & 1.834 &   965.4 & 1.728 \\
\bottomrule
\end{tabular}
\end{table}

@@

@@

We studied the effect of temperature, oxygen partial pressure and growth time towards \ce{MoO3} deposition on glass substrates. Each factor is divided into two levels, with T at 700 and 800, \ce{O2} at 1 and 10 sccm, and growth time of 15 and 60 mins. We will assign $+$ and $-$ to higher and lower levels, respectively. And the morphological variation is summarized in Table~\ref{tab:mo3glass}. 
% glass growth matrix 
\begin{table}[htb]
\centering
\caption{\ce{MoO3} growth on glass}\label{tab:mo3glass}
\begin{tabular}{lccp{3in}}
\toprule
\multicolumn{3}{c}{Growth Conditions} \\
\cmidrule(l){1-3}
 Temperature & \ce{O2} & Time & Morphology  \\
\midrule
-    &  +   & -  &   \\
-    &  -   & +  &   \\
+    &  +   & -  &   \\
+    &  +   & -  &   \\
+    &  +   & -  &   \\
+    &  +   & -  &   \\
\bottomrule
\end{tabular}
\end{table}

% droplet position statistics
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{droplets_sta}
\caption[Droplet position statistics]{Droplet position statistics. On-tip and not-on-tip counts variation with respect to growth time. }
\label{fig:mo3dropsta}
\end{figure}

@@

\cite{Chen2013j} To develop large-size single-crystal graphene on dielectric substrates. small carbon flow near-equilibrium CVD process. Grain size about 10 microns, precursor \ce{CH4} and \ce{H2} (ratio 2.3:50) at 1180 C. \ce{SiO2}-Si surface roughness. Although the growth substrates (quartz,\ce{SiO2}-Si and \ce{Si3N4}-\ce{SiO2}-Si ) have a complicated stereo network similar to diamond, regular hexagonal G growth is obtained, which indicates the deposition is determined by equilibrium kinetics, and this should be applicable to other 2D materials as well. I2D/IG exceeds two on \ce{SiO2}-Si subs (514.5nm), indicating monolayer G. armchair (AC) G edge grows faster than zigzag (ZZ) edge.

\cite{Weatherup2013} catalytic graphitization of solid carbon sources. catalytic transformation, the source is in solid state, low temperature (less than 600C), 2nm  \ce{Al2O3} by ALD as carbon diffusion barrier. amorphous silicon (a-Si), Ni lower the activation barrier ,  tetrahedral amorphous carbon (ta-C).

\cite{Bangert2013} low energy (50eV) ion implantation doping in G. Ions penetrate pristine G at energy larger than 100eV. Individual substitutional incorporation of B into G lattice is demonstrated. 1\% doping level was obtained.

\cite{Wu2013b} CVD G on copper. Size of single crystal domain and nucleation site density.

### 2014-02-15 ch-tms/tms.tex
daily works

The $E$ type phonon branches correspond to the in-plane normal modes, while the $A$ type phonons result from the out-of-plane vibrations. $A_{1g}$ mode is an out-of-plane vibration involving only the S atoms while the $E_{2g}^1$ mode involves in-plane displacement of transition metal and S atoms. The $E_{2g}^2$ mode is a shear mode corresponding to the vibration of two rigid layers against
each other and appears at very low frequencies ($<50 cm^{-1}$ \cite{Zhang2013i}). The $E_{1g}$ mode, which is an in-plane vibration of only the S atoms, is forbidden in the backscattering Raman configuration. In 2H type TMDC, the $A_{1g}$ mode is sensitive to electrostatic doping, while $E_{2g}^1$ mode is sensitive to strain, in which the FWHM of the peaks are indicator of external force quantity.

@@

Raman conditions: 0.3 mW, 532 nm, 200 sec acquisition time.

@@

\cite{Tenne2010} chemical modification of NTs. Functional ligand consists of an anchor group that attaches to the NTs surface and a tail which render them soluble in various solvents. PTAS functionalized BN nanotube lead to the formation of stable suspensions in aqueous solutions. The strong attachment is formed through $\pi-\pi$ interactions. ref 49, 416 cm raman on WS2. B1u is pressure sensitive.

@@

direct gap of ML at point K.

>>>>

The $E$ type phonon branches correspond to the in-plane normal modes, while the $A$ type phonons result from the out-of-plane vibrations. $A_{1g}$ mode is an out-of-plane vibration involving only the S atoms while the $E_{2g}^1$ mode involves in-plane displacement of transition metal and S atoms. The $E_{2g}^2$ mode is a shear mode corresponding to the vibration of two rigid layers against
each other and appears at very low frequencies ($<50 cm^{-1}$ \cite{Zhang2013i}). The $E_{1g}$ mode, which is an in-plane vibration of only the S atoms, is forbidden in the backscattering Raman configuration. In 2H-type TMDC, the $A_{1g}$ mode is sensitive to electrostatic doping, while $E_{2g}^1$ mode is sensitive to strain, in which the FWHM of the peaks are indicator of external force quantity.

@@

Raman conditions: 0.3 mW, 532 nm, 200 sec acquisition time. photon flux = $0.3E-3\times6.242E+18/1.2398/0.532=2.84E15$

@@

\cite{Tenne2010} chemical modification of NTs. Functional ligand consists of an anchor group that attaches to the NTs surface and a tail which render them soluble in various solvents. PTAS functionalized BN nanotube lead to the formation of stable suspensions in aqueous solutions. The strong attachment is formed through $\pi-\pi$ interactions.

416 cm raman on WS2. B1u is pressure sensitive. \cite{Staiger2012} also studied pressure dependence.

\cite{Zou2007} prepared W/\ce{WS2} core-shell NPs by reaction of tungsten and sulfur under hydrogen atmosphere. The shoulder mode under A1g is attributed to LA+TA. As pressure increase from 0GPa to 18GPa, these two bands, both shifting to higher wavenumbers, first separate and then recombine. It was assumed the compression mainly occurs in c axis, so the stiffening of A1g is anticipated.

@@

\cite{M2013} temperature dependent of ML \ce{WS2}. Interestingly in this report 2LA/A1g (514 nm) seems less than unit. The spectra were obtain from mechanically exfoliated \ce{WS2} lying on 300 \ce{SiO2}-Si substrate.  When the temperature increase from 77K to 623K, A1g shift from 420 to 416.5 cm.

direct gap of ML at corner of BZ, point K.
